---
title: "FarsFunctions: How to use Guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning=FALSE}
library(farsFunctions) 

```

## Introduction

<strong> Read through each of the functions documentation to see how they work </strong>

<p> The functions in this package are designed to help extract FARS data to produce a visual plot with a state map including the accidents location by year </p>

### List of Functions:

#### 1) fars_read 

This function reads data from .csv file, stored on disk, from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System (FARS), which is a nationwide census, providing the American public yearly data, regarding fatal injuries suffered in motor vehicle traffic crashes.

``` {r}
# fars_read("enter linelist here")
```

#### 2) make_filename

Make .csv data file name related to the given year The function does not check if the file is available.

``` {r}
make_filename(2013)
```

#### 3) fars_read_years

Ancillary function used by fars_summarize_years

``` {r}
#fars_read_years(2013)
```

#### 4) fars_summarize_years

This function summarizes yearly accidents data, by month

``` {r}
#fars_summarize_years(2013)
```

#### 5) fars_map_state

Displays a plot with a state map including the accidents location by year If the state.num is invalid the function shows an error.
